Concurrent Programming with Harmony

### 2020-07-27 book/paper.tex
Fixed formatting

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
tas(\textit{lk}) & test-and-set on \texttt{!{}}\textit{lk} \\
\hline
Lock() & return a lock object \\
\hline
lock(\textit{lk}) & acquire \texttt{!{}}\textit{lk} \\
\hline
unlock(\textit{lk}) & release \texttt{!{}}\textit{lk} \\
\hline
Condition(\textit{lk}) & return a condition variable on \texttt{!{}}\textit{lk} \\
\hline
wait($c$) & wait on condition variable \texttt{!{}}$c$ \\
\hline
notify($c$) & notify a process waiting on condition variable \texttt{!{}}$c$ \\
\hline
notifyAll($c$) & notify all processes waiting on condition variable \texttt{!{}}$c$ \\
\hline
Semaphore(\textit{cnt}) & return a semaphore object initialized to \textit{cnt} \\
\hline
P(\textit{sema}) & procure \texttt{!{}}\textit{sema}  \\
\hline
V(\textit{sema}) & vacate \texttt{!{}}\textit{sema}  \\
\hline
Queue() & return a synchronized queue object \\
\hline
dequeue($q$) & return next element of $q$, blocking if empty \\
\hline
enqueue($q$, \textit{item}) & add \textit{item} to $a$ \\
\hline
\end{tabular}

>>>>

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{tas}(\textit{lk}) & test-and-set on \texttt{!{}}\textit{lk} \\
\hline
\texttt{Lock}() & return a lock object \\
\hline
\texttt{lock}(\textit{lk}) & acquire \texttt{!{}}\textit{lk} \\
\hline
\texttt{unlock}(\textit{lk}) & release \texttt{!{}}\textit{lk} \\
\hline
\texttt{Condition}(\textit{lk}) & return a condition variable on \texttt{!{}}\textit{lk} \\
\hline
\texttt{wait}($c$) & wait on condition variable \texttt{!{}}$c$ \\
\hline
\texttt{notify}($c$) & notify a process waiting on condition variable \texttt{!{}}$c$ \\
\hline
\texttt{notifyAll}($c$) & notify all processes waiting on condition variable \texttt{!{}}$c$ \\
\hline
\texttt{Semaphore}(\textit{cnt}) & return a semaphore object initialized to \textit{cnt} \\
\hline
\texttt{P}(\textit{sema}) & procure \texttt{!{}}\textit{sema}  \\
\hline
\texttt{V}(\textit{sema}) & vacate \texttt{!{}}\textit{sema}  \\
\hline
\texttt{Queue}() & return a synchronized queue object \\
\hline
\texttt{dequeue}($q$) & return next element of $q$, blocking if empty \\
\hline
\texttt{enqueue}($q$, \textit{item}) & add \textit{item} to $a$ \\
\hline
\end{tabular}
